A New Metric for the Analysis of Swarms

### 2018-06-13 paper.tex
Future

The two metrics together provide a deeper evaluation of a swarm's structure and `potential' thean either of the metrics alone. Consider the following: the repulsion field is increased but the internal distances do not change; as a result the \emph{cohesion/repulsion metric} rises. This indicates `something' is confining the swarm's distribution as discussed in Section \ref{metric:ApplicationFloodFilling}. This analysis could be used in identifying effective swarm distribution for the coverage of a sensor array as discussed by Ramaithitima et al.~\cite{RWBK:15}

>>>>

The two metrics together provide a deeper evaluation of a swarm's structure and `potential' than either of the metrics alone. Consider the following: the repulsion field is increased but the internal distances do not change; as a result the \emph{cohesion/repulsion metric} falls below zero. This indicates `something' is confining the swarm's distribution as discussed in Section \ref{metric:ApplicationFloodFilling}. This analysis could be used in identifying effective swarm distribution for the coverage of a sensor array as discussed by Ramaithitima et al.~\cite{RWBK:15}
